Empowering the use of community driven preprints in ecology and evolution

### 2024-04-17 ms/ms.qmd
Adding in the correct informatino for published date for preprints as the current column has misisng data, and that cannot be possible

# Delegate details
  delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")

  del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
			mutate(attend = str_to_title(attend))  %>% tabyl(attend)

# Master preprint list
  master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()

# Check allocation of papers
		contr_extract <- master_list  %>%  tabyl(extractor_full_name)

	# Check how many each person has done relative to their total
		contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)

# raw data. For analysis
	data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")

@@

@@

  p1 <- ggplot(data2, aes(x = preprint_published_date)) +
    geom_histogram(fill = "black", color = "black") +
    labs(x = "Published Date", y = "Number of Papers") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

@@

To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.  *EcoEvoRxiv* accepts both preprints and postprints. Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal. Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication. For the purpose of summarising articles on *EcoEvoRxiv* we include these in our analysis.

@@

Gender differences in preprint use have been established in a number of other research fields. It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison]. Understanding gender publishing patterns is challenging. We cannot know the gender of authors for certainty but we can use a data driven approach to suggest the probability that a particular name is of a given gender (male or female). We used the R package *DemografixeR* (vers. `r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint. We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming.

>>>>

# Delegate details
  #delegates <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Delegate Details")

  #del_details <- delegates  %>% rename("attend" = "Attended hackathon (yes/no)") %>%
			mutate(attend = str_to_title(attend))  %>% tabyl(attend)

# Master preprint list
  #master_list <- read_sheet("https://docs.google.com/spreadsheets/d/1UEAUZWpOm7C1kKoVoYy-u_D6cbHoF--EGxoY0Gl0qHw/edit#gid=836736319", sheet = "Master List of Preprints") %>% clean_names()

# Check allocation of papers
		#contr_extract <- master_list  %>%  tabyl(extractor_full_name)

	# Check how many each person has done relative to their total
		#contr_extract2 <- master_list %>% group_by(extractor_full_name) %>% summarise(n = n(), yes = sum(completed_yes_no_extractor == "Yes"), no = sum(completed_yes_no_extractor == "No"), prop = yes/n)  %>% data.frame()  %>% arrange(n)

# raw data. For analysis
	#data_coll <- read_sheet("https://docs.google.com/spreadsheets/d/1032gLryvtCNJ7eJjKBjrn7txxDRUGql9SoIG18QnFrQ/edit?resourcekey#gid=1062856014")

@@

# Seem to be missing the publication date for preprints and this should ne known for all
    data3 <- read_excel(here("data", "20231003_EER_preprints_metadata.xlsx"))  %>% clean_names()

	# Subset the relevant rows
		data3  <- data3  %>%  dplyr::select(preprint_id, preprint_doi, publisher_doi, published_date)  %>% rename("preprint_published_date" = "published_date" )

  # Merge with the main data to make sure that the published data of the preprint is known for ALL papers
    data2  <- left_join(data2, data3, by = c("preprint_id" = "preprint_id"))

@@

  p1 <- ggplot(data2, aes(x = preprint_published_date.y)) +
    geom_histogram(fill = "black", color = "black") +
    labs(x = "Published Date", y = "Number of Papers") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(plot.tag = element_text(size = 16, face = "bold"), plot.tag.location = "margin")

@@

To better understand preprint (and postprint) use on *EcoEvoRxiv*, we downloaded metadata on the articles available on *EcoEvoRxiv* as of `r gsub("UTC", "", dates[2])`.  *EcoEvoRxiv* accepts both preprints and postprints. Postprints are articles that are already published but are the final version of the published paper before typesetting for the research journal. Postprints are a useful way to ensure published articles are openly accessible and can be posted anytime after publication (assuming the journal has a preprint policy). For the purpose of summarising articles on *EcoEvoRxiv* we include these in our analysis.

@@

Gender differences in preprint use have been established in a number of other research fields. It is hypothsised that such differences are driven by the larger childcare burden of female researchers, which limit their abilities to publish as frequently as their male counterparts [@ucar2022mind; @wehner2020comparison]. Understanding gender publishing patterns is challenging with observational data. We cannot know the gender of authors for certainty but we can use a data driven approach to ascertain the probability that a particular name is of a given gender (male or female). We used the R package *DemografixeR* (vers. `r utils::packageVersion("DemografixeR")`; @RJ-2016-002) to predict the most likely gender of the submitting author of a preprint. We incorperated information about the submitting authors country of affiliation to better account for differences across countries in naming. We only used names where the gender was identified with 95% certainty.
